---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# xcursion

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

`xcursion` is a package that uses the headers from [`xtensorrr`](https://github.com/DavisVaughan/xtensorrr) to show off a 
few examples using `xtensor` and `xtensor-r`.

## Installation

``` r
devtools::install_github("DavisVaughan/xcursion")
```

## Example

```{r}
library(xcursion)
```

Just get a 2x2 numeric matrix back
from an `xarray<double>`. There is some
dynamic sizing happening here

```{r}
two_by_two_rarray()
```

Just get a 2x2 numeric matrix back
from an xtensor<double, 2>
you have to be more explicit about
sizing here

```{r}
two_by_two_rtensor()
```

Add 1 to an R object
Using xarray means the dimensions are
determined dynamically

```{r}
plus_one(c(1, 2))

plus_one(matrix(c(1, 2)))

plus_one(array(1, dim = c(2, 2, 2)))
```

```{r}
# Interestingly, I think ALTREP breaks some of this
plus_one(1:5)

plus_one(1:5 + 1) # <- this is fine
```

Broadcastable sum

```{r}
vec <- c(1, 2, 3, 4, 5)
m1 <- matrix(vec, ncol = 1)
m2 <- matrix(vec * 2, ncol = 1)

m3 <- cbind(m1, m2)

# Adding two matrices normally
xt_sum(m1, m2)

# Colwise broadcast
xt_sum(m1, m3)

# Outer sum
xt_sum(m1, t(m1))

# A vector is a 1 row matrix
# so we get the same result as above
xt_sum(m1, vec)

```

